\documentclass[8pt]{extarticle}
\input{common.tex}

\def\boxpad{4pt}
\tcbsetforeverylayer{left=\boxpad,right=\boxpad,top=\boxpad,bottom=\boxpad}

\begin{document}
\thispagestyle{empty}

\begin{center}
  {\LARGE
  Essential Software Engineering for Researchers - Lesson 1 - URL: v.gd/softeng}
\end{center}

\subsection*{Tools}

\begin{navybox}[title=Virtual Environments]
  Self contained environments where you can install dependencies for an
  individual project. Make your work more portable and reproducible. We
  recommend \textbf{conda}, a package manager that supports virtual environments
  and multiple languages. Record the packages you want in an environment.yml
  file.\par
  \vspace{5pt minus 3pt}

  \boxed{2}{Create a new environment}{
    conda env create -f environment.yml
  }
  \quad
  \boxed{2}{Update an existing environment}{
    conda env update -f environment.yml
  }
  \vspace{5pt minus 3pt}

  Remember to \textbf{activate} your environment or configure your IDE in order
  to use it.
\end{navybox}

\begin{bluebox}[title=Code Formatters]
  A tool, such as \textbf{black}, to format your code for consistency and
  convenience. Configure your IDE to automatically apply formatting when you
  save a file.  See https://github.com/rishirdua/awesome-code-formatters for
  many different languages.
\end{bluebox}

\begin{navybox}[title=Linters]
  Use a linter to enforce a consistent style, catch simple errors quickly and
  keep your code tidy. Integrate with your IDE to get instant feedback as you
  type. See https://github.com/caramelomartins/awesome-linters for many
  different languages.
\end{navybox}

\subsection*{Techniques}

\begin{bluebox}[title=Data Structures]
  The same data can be stored and manipulated in different ways by different
  data structures. Think carefully about which data structure is best suited to
  your problem. To simplify your code you can create new data structures.
\end{bluebox}

\begin{navybox}[title=Structuring Code]
  \boxed[equal height group=A]{3}{Levels of abstraction}{Different parts of
    your code should deal with different levels of detail. Don't mix different
    levels!}
  \boxed[equal height group=A]{3}{Separation of Concerns}{The discrete tasks
    carried out by your code should be separated as much as is possible.}
  \boxed[equal height group=A]{3}{Dataflow}{The movement and transformation of
    data within your code should be reflected in its structure.}
\end{navybox}

\begin{bluebox}[title=Design Patterns]
  A transferable solution to a commonly encountered problem. There are very many
  patters and the trick is finding the right one. Iterators are a pattern used
  to separate loops from compute. Dependency injection is a pattern to create
  modular algorithms.
\end{bluebox}

\furtherhelp

\end{document}
